Income Has Serious Implications On Many Facets of American Life in 2021

### 2022-03-22 outputs/paper/paper.Rmd
FINAL COMMIT

---
title: "Income Has Serious Implications On Many Facets of American Life in 2021"
subtitle: "A Look Into The Implications of Americans' Incomes Reveals Information On The Veracity of American Dream."
author: 
  - Adam Labas  
  - Krupali Bhavsar
thanks: "Code and data are available at: https://github.com/adam-labas/The-US-GSS-And-The-American-Dream"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2
toc: TRUE
bibliography: references.bib
---

@@

If you ask a group of first graders what they aspire to be when they grow up, it wouldn't be surprising to hear a lot of kids say that they would want to be the richest person in the world. For as long as humanity has existed, the allure and pride associated with wealth and the accumulation of large sums of wealth has always been at the forefront of the social and economic paradigm. Whether it was Mansa Musa in East Africa in the 14th century or Jeff Bezos today, the wealthy have always stood out in large crowds. This aspect of the social sphere is one that can undoubtedly be found in American livelihood. It would be hard to deny for any of us that money rules the world, regardless of how we feel about that. We need it to put food on our tables, clothes on our backs and seemingly to increase our quality of life. As such, it would appear as if a surplus of money in ones possession could do no harm.

For the last 50 years, people from all over the world have began to flock to the United States as immigrants in search of the so called American Dream. The American Dream is a Utopian idea in which the United States of America is a safe haven for all those looking to improve their quality of life via monetary gain. It implies that anyone (yes, absolutely anyone) who is willing to put in the hard work required to be successful, will have much improves abilities to make something of themselves in the United States than they could elsewhere, all else being equal.

In this analysis, we got our hands on some of the 2021 United States General Social Survey data which is described with great extent in the Data Section \@ref(data). In our analysis, we decided to focus on how the various factors and trends in the data in order to try and gather some implications on the veracity of the american dream. To further break down the analysis, we decided to look into the distribution of the aforementioned data by segregating the data not only by the current income of respondents but also by their income at age 16, and trying to see if we can spot any relation between an increase in income from age 16 to now and the gender, or the number of grandparents of the respondent, born in the United States.

In this paper, we will attempt to take you on a journey to explore the data that was used to produce the findings, we will visually present to you the findings and we will speak about the implications of the findings and later on in the Limitations Section \@ref(limitations), we will discuss the limitations of our data and problems that this may have when wanting to extract true, ethical, unbiased information from the implications of the findings.

@@

## Problem With Data Upload into R Studio
We know that having a reproducible workflow is crucial if we want to produce mature and ethical statistical papers which any data scientist down the line can reproduce for any purpose from verifying results or modifying methodology. As previously stated, the raw data provided by the United States 2021 General Social Survey was in a zip folder and in dta format. To conduct the development of this paper, we worked in RStudio {@citeR) in a server developed, maintained an administered by one of the TAs for the STA304 Course at the University of Toronto (Winter 2022), Mauricio Vargas Sepúlveda, better known as Pachá. This server works just like any other server for RStudio like JupyterHub but the admin user, Pachá, has the ability to overview all activity on the server and access users accounts to aid with trouble shooting or data sharing: this will proved to be decisive in just a moment. When we tried to follow typical procedure to upload the 2021_stata.zip file into under data in the inputs folder, we received a message we had never received before. Figure 1 is a screen capture of that error.
![The Error received upon attempting to upload the zip folder](~/paper_3_team_paper/inputs/2021_stata_error_message.png "The error message we received when trying to upload the zip folder.")

@@

# Appendix {-}

>>>>

---
title: "Income Has Serious Implications On Many Facets of American Life in 2021"
subtitle: "A Look Into The Implications of Americans' Incomes Reveals Information On The Veracity of American Dream."
author: 
  - Adam Labas  
  - Krupali Bhavsar
thanks: "Code and data are available at: https://github.com/adam-labas/The-US-GSS-And-The-American-Dream"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "The American Dream is the idea that, as a nation, the United States embodies freedom that includes financial success, upward social mobility for families and children, as well as freedom to live as they please in a society with few barriers. We obtained and analyzed data from the 2021 United States General Social Survey, focusing on the relationship between the distribution of past and present income and various external demographic categories. We find that the data’s limitations limit our findings, where the analysis points to a heavy skew in income across all demographics however, the uneven bin width, income cutoff and small sample size obstruct us from taking our implications at face value. Although our findings have implications for the theory of the American Dream, due to the limitations we choose to create a stand alone supplementary survey that will aid us for our purposes."
output:
  bookdown::pdf_document2
toc: TRUE
bibliography: references.bib
---

@@

If you ask a group of first graders what they aspire to be when they grow up, it wouldn't be surprising to hear a lot of kids say that they would want to be the richest person in the world. For as long as humanity has existed, the allure and pride associated with wealth and the accumulation of large sums of wealth has always been at the forefront of the social and economic paradigm. Whether it was Mansa Musa in East Africa in the 14th century or Jeff Bezos today, the wealthy have always stood out in large crowds. This aspect of the social sphere is one that can undoubtedly be found in American livelihood. It would be hard fro any of ud to deny that money rules the world, regardless of how we feel about that. We need it to put food on our tables, clothes on our backs and seemingly to increase our quality of life. As such, it would appear as if a surplus of money in ones possession could do no harm.

For the last 50 years, people from all over the world have began to flock to the United States as immigrants in search of the so called American Dream. The American Dream is a Utopian idea in which the United States of America is a safe haven for all those looking to improve their quality of life, via monetary gain. It implies that anyone (yes, absolutely anyone) who is willing to put in the hard work required to be successful, will have much improves abilities to make something of themselves in the United States than they could elsewhere, all else being equal.

In this analysis, we got our hands on some of the 2021 United States General Social Survey data which is described with great extent in the Data Section \@ref(data). In our analysis, we decided to focus on  the various factors and trends in the data in order to try and gather some implications on the veracity of the American Dream. To further break down the analysis, we decided to look into the distribution of the aforementioned data by segregating the data not only by the current income of respondents but also by their income at age 16, and trying to see if we can spot any relation between an increase in income from age 16 to now and the gender, or the number of grandparents of the respondent, born in the United States.

In this paper, we will attempt to take you on a journey to explore the data that was used to produce the findings, we will visually present to you the findings and we will speak about the implications of the findings and later on in the Limitations Section \@ref(limitations), we will discuss the limitations of our data and problems that this may have, when wanting to extract true, ethical, unbiased information from the implications of the findings.

@@

## Problem With Data Upload into R Studio
We know that having a reproducible workflow is crucial if we want to produce mature and ethical statistical papers which any data scientist down the line can reproduce for any purpose from verifying results or modifying methodology. As previously stated, the raw data provided by the United States 2021 General Social Survey was in a zip folder and in dta format. To conduct the development of this paper, we worked in RStudio {@citeR) in a server developed, maintained an administered by one of the TAs for the STA304 Course at the University of Toronto (Winter 2022), Mauricio Vargas Sepúlveda, better known as Pachá. This server works just like any other server for RStudio like JupyterHub but the admin user, Pachá, has the ability to overview all activity on the server and access users accounts to aid with trouble shooting or data sharing: this will proved to be decisive in just a moment. When we tried to follow typical procedure to upload the 2021_stata.zip file into under data in the inputs folder, we received a message we had never received before. Figure 1 bellow is a screen capture of that error.

![The Error received upon attempting to upload the zip folder](~/paper_3_team_paper/inputs/2021_stata_error_message.png "The error message we received when trying to upload the zip folder."){.center}

@@

# Appendix {-}
Below is a link and a QR code for the supplementary survey alluded to in Section \@ref(next-steps).

LINK TO SURVEY: https://docs.google.com/forms/d/1a3tK-uSkl0MDrjqxWW1aCKhLowQxdqBvE6Bid6wN3YY/edit?ts=6239fa2b

![Supplimentary Survey](~/paper_3_team_paper/inputs/Supplimentary_survey_QR.png){width="300" height="500"}
